plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-10-09 manuscript.Rmd
Semi-working remake workflow

# Find current SHA of plantecophys
rep_pkg <- "c:/repos/plantecophys"
if(file.exists(rep_pkg)){
  pkgrep <- repository(rep_pkg)
  r <- reflog(pkgrep, verbose=FALSE)
  cur_sha <- substr(r[[1]]@sha, 1, 7)
} else {
  cur_sha <- "???"
}

# Analysis for Figure 5.
source("R/analysis.R")

# Make PDFs
source("R/make_figures.R")

# This document can be compiled with the 'Knit Word' button in Rstudio, or:
# library(rmarkdown)
# render("manuscript.Rmd", "word_document", "manuscript.docx")
```

@@

\
**Figure 5**. Example application of the plantecophys package to A-C~i~ curves and spot gas exchange measurements on *Eucalyptus delegatensis* (data can be downloaded from [@medlynfigshare]) (a) Fitted A-C~i~ curves with one curve highlighted (b) Estimates of J~max~ plotted against V~cmax~, obtained from the fitted curves in panel (a). Solid line is a regression line (J~max~ = `r round(lmjvt$estimate[1],2)` + `r signif(lmjvt$estimate[2],2)` V~cmax~, R^2^ = `r signif(lmjvg$r.squared,2)`) with a 95% confidence interval for the mean. (c) Modelled (with the model of Medlyn et al. 2011) versus measured g~s~ (p `r pval(lmgpredg$p.value)`, R^2^ = `r signif(lmgpredg$r.squared,2)`). Measurements included a wide range of environmental conditions (PAR, T~leaf~, D). In this example, only g~1~ was fit (estimate = `r signif(g1,3)`, 95% CI = `r paste(signif(g1ci,3), collapse=" - ")`). (d) The predicted response of ITE (A~n~ / E) as a function of D from the fitted model in panel (c) (solid line), and the measurements from panel (c) when PAR > 1000.

>>>>

# Find current SHA of plantecophys
rep_pkg <- "c:/repos/plantecophys"
if(file.exists(rep_pkg)){
  pkgrep <- repository(rep_pkg)
  r <- reflog(pkgrep, verbose=FALSE)
  cur_sha <- substr(r[[1]]@sha, 1, 7)
} else {
  cur_sha <- "???"
}
# 
# # Some summaries of stats for Figure 5.
# gfit <- fitBB(tumspot, gsmodel="BBOpti")
# tumspot$GSpred <- predict(gfit$fit, tumspot)
# g1 <- coef(gfit)[[2]]
# g1ci <- suppressMessages(unname(confint(gfit$fit)))
# 
# lmgpred <- lm(Cond ~ GSpred, data=tumspot)
# lmgpredt <- tidy(lmgpred)
# lmgpredg <- glance(lmgpred)
# 
# # Regression of Jmax vs. Vcmax (used in caption for Figure 5).
# p <- coef(acifits)
# lmjv <- lm(Jmax ~ Vcmax, data=p)
# lmjvt <- tidy(lmjv)
# lmjvg <- glance(lmjv)

acifits <- readRDS("cache/acifits.rds")

@@
